---
title: "Weight of Fish"
author: "Cesar Guillen"
date: "Summer 2022"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```


```{r}
All_Fish <- read.csv(file="Fish.csv")
```

```{r}
Perch <- filter(All_Fish,Species=="Perch")
```

```{r}
Perch <- select(Perch, -Species)
```


# Predicting Fish Weight

## Perch

```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models

The best model for Perch would be Height and Width. 

### Best Two regressor model

The best two regressor models would also be Height and Width. 

## Pike

```{r}
Pike <- filter(All_Fish,Species=="Pike")
```

```{r}
Pike <- select(Pike, -Species)
```

```{r}
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Models

The best models would be Length 1, Length 2, Length 3, Height, and Width since they are all near the top of the model above.  

### Best Two regressor model

The best two Regressor models would be Length 1 and Length 3, because they are both on the two together are the best explanatory variables to go by. 
## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements